Network Fusion through CDRP Model\\ Decomposition and Assembly

### 2020-01-10 paper/paper.tex
cdrp fix typo

Critical Data Routing Path is a method to find a path containing critical nodes, whose removal causes great preformance setback, from a existing trained model. We introduce CDRP to decomposite one existing pretrained model from selecting representing CDRPs in a given dataset.

@@

Critical data routing path is extracted through optimizaition of control gates values. We freeze the weights of the model, and for each sampe we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values. The gate values can be concatenated into one single vector as representation of that sample. As the original paper \cite{wang2018interpret} states, these gate values encode patterns inside the input images, e.g. tinca in horizontal positions or squat positions will have different encodings.

>>>>

Critical Data Routing Path is a method to find a path containing critical nodes, whose removal causes great preformance setback, from an existing trained model. We introduce CDRP to decomposite one existing pretrained model from selecting representing CDRPs in a given dataset.

@@

Critical data routing path is extracted through optimizaition of control gates values. We freeze the weights of the model, and for each sample we follow the procedure of Distillation Guided Routing (algorithm \ref{alg:dgr}) \cite{wang2018interpret} to get the gate values. The gate values can be concatenated into one single vector as representation of that sample. As the original paper \cite{wang2018interpret} states, these gate values encode patterns inside the input images, e.g. tinca in horizontal positions or squat positions will have different encodings.
